---
title: "Unit 1 - 3 Review Starter"
author: "Vishal, Ian and Shamya"
date: "Insert date here"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sites <- read_csv("data/sand_minerals.csv")
location_descriptions <- read_csv("data/location_descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility_hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals}
glimpse(sites)
#There are 23 rows and 2 variables (columns) in the data.
#Each row stats the location and type of mineral at that specific location. 
names(sites) #completed the names() command
```


### Exercise 2
```{r inspect-other-dataframes}
glimpse(density)
glimpse(location_descriptions)
glimpse(solubility_hardness)
#Density has 3 rows and 2 variables, each row stats the density and name of mineral.
#Location_description has 10rows and 2 variables, each row stats the location identifier and the description of that location.
#Solubility_hardness has 3 row and 3 variables, each row stats the harness, solubility of each mineral.
names(density)
names(location_descriptions)
names(solubility_hardness)
```

### Exercise 3

```{r stitch}
sites_mineral_densities <- sites %>% left_join(density)
sites_mineral_densities
#There are 23 rows in sites_mineral_densities.
sand_mineral_properties <- sites_mineral_densities %>% left_join(solubility_hardness)
sand_mineral_properties
```

### Exercise 4
```{r sorting sand grains by location}
sand_mineral_properties %>%
  count(location)
```

```{r last 10}
sand_mineral_properties %>%  
  slice_tail(n = 10)
```

```{r new order}
sand_mineral_properties %>% 
  arrange(desc(density)) %>%
  slice_tail(n = 10)
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

## Part II - Data Visualization

`starwars` is already loaded within the `dplyr` package (within `tidyverse`)

### Exercise 7

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 8

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 9

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
